Developing a preprint culture in biology

### 2012-09-29 ms.tex
formatting, bib file

\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys]{revtex4-1}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\hypersetup
{
    colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

@@

\author{Karthik Ram}
\affiliation{Environmental Science, Policy, and Management. University of
California, Berkeley. Berkeley, CA. United-States of America.}

@@

\keywords{Publishing; preprint server; Green Open Access; arXiv.}

@@

PDP is supported by an Alexander Graham Bell scholarship from the National
Sciences and Engineering Council of Canada. JJA is supported by NSF DEB-0614166
and NSF DEB-0919018. DG is funded by a Discovery Grand from the National
Sciences and Engineering Council of Canada and by the Canada Research Chair
program.

@@

\newpage
\bibliography{refs}
\bibliographystyle{plain}

>>>>

\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys,longbibliography]{revtex4-1}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\hypersetup
{
    colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

@@

\author{Karthik Ram}
\affiliation{Environmental Science, Policy, and Management. University of California, Berkeley, United-States of America.}

@@

\keywords{Publishing; Preprint servers; Green Open Access; arXiv.}

@@

PDP is supported by an Alexander Graham Bell scholarship from the National
Sciences and Engineering Council of Canada. JJA is supported by NSF DEB-0614166
and NSF DEB-0919018. DG is funded by a Discovery Grand from the National
Sciences and Engineering Council of Canada and by the Canada Research Chair
program. EPW is supported by a CAREER Award from the National Science Foundation
(DEB-0953694).

@@

\newpage
\bibliography{refs}
